Classless Java

### 2016-03-21 OOPSLA16/sections/Overview.tex
Section 2 code style.

\lstinputlisting[linerange=8-10]{../UseMixinLombok/src/pegasus/simple/lombok/Main.java}% APPLY:linerange=PEGASUS_LOMBOK
\bruno{I dislike the code formating here.}
\noindent The effect of the annotations is that a static \emph{factory} method called
\texttt{of} is automatically added to the interfaces. With the
\texttt{of} method a \texttt{Pegasus} object is instantiated as follows:

@@

\begin{lstlisting}
Point2D p = new Point2D() {
  int x(){return 4;} public int y(){return 2;}  }
\end{lstlisting}

@@

\paragraph{\texttt{with-} methods in object interfaces}
The pattern of creating a new object by reusing most information from an old
object is very common when programming with immutable
data-structures. As such, it is
supported in by \mixin as \Q@with-@ methods. For example:
\begin{lstlisting}
@Obj interface Point2D {
    int x();    int y(); // getters
     //with methods
    Point2D withX(int val);    Point2D withY(int val);
}
\end{lstlisting}

@@

%Now we proceed to define \texttt{Animal} with \texttt{point} ``member
%field''.
%%Not again, before we used only getters!
% Again, we model this member field with getter and setter methods:
\lstinputlisting[linerange=58-58]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=ANIMAL

@@

\lstinputlisting[linerange=62-63]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=HORSE

@@

\lstinputlisting[linerange=67-70]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD
\bruno{Don't like the code format here either.}
%Interface \texttt{Point3D} extends \texttt{Point2D} with a new abstract method
%\texttt{int z()} (treated as a getter for member field \texttt{z}). Note that
%the return type of various methods (e.g. with- methods, getters) get refined
%either by covariant method overriding or automatically by our annotation
%processor. Besides \emph{with}, other methods (including \emph{clone},
%\emph{of}) also do type-refinements automatically.

@@

\begin{figure}
\marco{I can not find the declaration int x();
also we can change the order of the code to write the non generated stuff first.}
\saveSpaceFig
\lstinputlisting[linerange=79-91]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=GENERATED_POINT3D
\caption{Generated boilerplate code.}
\label{fig:boilerplate}
\end{figure}

@@

\lstinputlisting[linerange=74-74]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

@@

\lstinputlisting[linerange=58-58]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=ANIMAL

\lstinputlisting[linerange=62-63]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=HORSE

\lstinputlisting[linerange=67-70]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=74-74]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

>>>>

\lstinputlisting[linerange=8-12]{../UseMixinLombok/src/pegasus/simple/lombok/Main.java}% APPLY:linerange=PEGASUS_LOMBOK
\bruno{I dislike the code formating here.}
\noindent The effect of the annotations is that a static \emph{factory} method called
\texttt{of} is automatically added to the interfaces. With the
\texttt{of} method a \texttt{Pegasus} object is instantiated as follows:

@@

\begin{lstlisting}
Point2D p = new Point2D() {
  int x() {return 4;}
  public int y() {return 2;}
}
\end{lstlisting}

@@

\paragraph{\texttt{with-} methods in object interfaces}
The pattern of creating a new object by reusing most information from an old
object is very common when programming with immutable
data-structures. As such, it is
supported in by \mixin as \Q@with-@ methods. For example:
\begin{lstlisting}
@Obj interface Point2D {
    int x();    int y(); // getters
    // with methods
    Point2D withX(int val);
    Point2D withY(int val);
}
\end{lstlisting}

@@

%Now we proceed to define \texttt{Animal} with \texttt{point} ``member
%field''.
%%Not again, before we used only getters!
% Again, we model this member field with getter and setter methods:
\lstinputlisting[linerange=58-60]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=ANIMAL

@@

\lstinputlisting[linerange=64-67]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=HORSE

@@

\lstinputlisting[linerange=71-80]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD
\bruno{Don't like the code format here either.}
%Interface \texttt{Point3D} extends \texttt{Point2D} with a new abstract method
%\texttt{int z()} (treated as a getter for member field \texttt{z}). Note that
%the return type of various methods (e.g. with- methods, getters) get refined
%either by covariant method overriding or automatically by our annotation
%processor. Besides \emph{with}, other methods (including \emph{clone},
%\emph{of}) also do type-refinements automatically.

@@

\begin{figure}
\marco{I can not find the declaration int x();
also we can change the order of the code to write the non generated stuff first.}
%\saveSpaceFig
\lstinputlisting[linerange=89-115]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=GENERATED_POINT3D
\caption{Generated boilerplate code.}
\label{fig:boilerplate}
\end{figure}

@@

\lstinputlisting[linerange=84-84]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS

@@

\lstinputlisting[linerange=58-60]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=ANIMAL

\lstinputlisting[linerange=64-67]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=HORSE

\lstinputlisting[linerange=71-80]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=84-84]{../UseMixinLombok/src/pegasus/TestAnimal.java}% APPLY:linerange=PEGASUS
